Variety in the Implementation of Nonlinear Least Squares Program Codes

### 2022-06-14 VarietyInNLS/VarietyInNonlinearLeastSquaresCodes.Rmd
Minor edits

- tools such as the `nls()` function in R has so many legacy uses that it is likely
  impossible to deprecate it. However, it has also (as we detail in ??RefactoringNLS??)
  non-maintainable, but it seems unlikely that any
  further development, nor even repair of current deficiencies, will be forthcoming.
  This underlines the importance of designing software for its long-term maintenance,
  and this is often inimical to using currently novel programming tools.

>>>>

- tools such as the `nls()` function in R has so many legacy uses that it is likely
  impossible to deprecate it. However, as we detail in a related article, "Refactoring 
  the `nls()` function in R" 
  <!-- ??RefactoringNLS??,  -->
  it is practically non-maintainable. It seems unlikely that any
  further development, nor even repair of current deficiencies, will be forthcoming.
  This underlines the importance of designing software for its long-term maintenance,
  and this is often inimical to using currently novel programming tools.
